**Density Dependence**

### 2023-02-18 Rmd/report mac.Rmd
with ref pts

source("../R/dd.R")
source("../R/pm.R")

source("../R/get_dropbox.r")
dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

@@

fig_nums(
  name    = "om_VPADDMMM", level = 1, display = FALSE,
  caption = "Simulation of density dependence in Mass-at-age, maturity at age and M at age")

@@

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_comparing_dd.jpg")))

>>>>

source("../R/dd.R")
source("../R/pm.R")
```

```{r}
source("../R/get_dropbox.R")

dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

@@

```{r, echo=FALSE, fig.width=0.6, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}
fig_nums(
  name    = "om_VPADDMMM", level = 1, display = FALSE,
  caption = "Simulation of density dependence in Mass-at-age, maturity at age and M at age")

@@

```{r, echo=FALSE, fig.width=0.6, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE, eval=FALSE}

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_comparing_dd.jpg")))
```
